---
author: "K. Fleetwood"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document:
    df_print: paged
title: "Baseline characteristics table for NSTEMI"
---
  
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(DBI)
library(dbplyr)
library(dplyr)
library(janitor)
library(knitr)
library(arsenal)
library(lubridate)
library(ggh4x) # hacks for ggplot

ccu046_folder <- "~/collab/CCU046"
ccu046_01_folder <- file.path(ccu046_folder, "CCU046_01")
bc_folder <- file.path(ccu046_01_folder, "baseline_characteristics")
cohort_folder <- file.path(ccu046_folder, "CCU046_02", "processed_data")
r_folder <- file.path(ccu046_folder, "r")

# Additional functions to help with rounding to 5
source(file.path(r_folder, "tableby_functions_19Jan24.R"))  
source(file.path(r_folder, "output_functions_11Jul24.R")) 
```

```{r load_data, include=FALSE}

cohort <- readRDS(file = file.path(cohort_folder, "01_cohort.rds"))

st_deviation_no <- c("No acute changes", "Left bundle branch block",
                     "T wave changes only", "Other acute abnormality")
cohort <- 
  cohort %>%
  mutate(
    st_deviation = 
      case_when(
        ecg %in% st_deviation_no  ~ "No",
        ecg %in% c("ST segment elevation", "ST segment depression") ~ "Yes",
        is.na(ecg) ~ as.character(NA)
      ), 
    crt_log = log(creatinine),
    mi_event_month = floor_date(mi_event_date, "month")
  )

# Smoking cessation
cohort <- 
  cohort %>%
  mutate(
    smoking_cessation_advice = 
      case_when(
        smoking_cessation_advice %in% "0. No" ~ "No",
        smoking_cessation_advice %in% "1. Yes" ~ "Yes",
        smoking_cessation_advice %in% "2. Planned in rehab" ~ "Planned in rehab",
        smoking_cessation_advice %in% "3. Not applicable" ~ "Not applicable",
        smoking_cessation_advice %in% "9. Unknown" ~ as.character(NA),
        TRUE ~ as.character(NA)
      ),
    smoking_cessation_advice = 
      factor(smoking_cessation_advice, levels = c("Yes", "Planned in rehab", "No", "Not applicable"))
  )

# Individual secondary prevention medications
med_lvls <- c("Yes", "Contraindicated", "Patient declined treatment", 
              "Not applicable", "Not indicated", "No")
cohort <- 
  cohort %>% 
  mutate(
    aspirin = substring(discharged_on_aspirin, 4, 100),
    aspirin = ifelse(aspirin %in% "Unknown", as.character(NA), aspirin),
    aspirin = factor(aspirin, levels = med_lvls),
    # 
    bb = substring(discharged_on_beta_blocker, 4, 100),
    bb = ifelse(bb %in% "Unknown", as.character(NA), bb),
    bb = factor(bb, levels = med_lvls), 
    # 
    statin = substring(discharged_on_statin, 4, 100),
    statin = ifelse(statin %in% "Unknown", as.character(NA), statin),
    statin = factor(statin, levels = med_lvls), 
    #
    ace = substring(discharged_on_ace_i, 4, 100),
    ace = ifelse(ace %in% "Unknown", as.character(NA), ace),
    ace = factor(ace, levels = med_lvls), 
    #
    thieno = substring(discharged_on_thieno_inhibitor, 4, 100), 
    thieno = ifelse(thieno %in% "Unknown", as.character(NA), thieno),
    thieno = factor(thieno, levels = med_lvls), 
    #
    tica   = substring(discharged_on_ticagrelor, 4, 100), 
    tica = ifelse(tica %in% "Unknown", as.character(NA), tica),
    tica = factor(tica, levels = med_lvls)
  )

labels(cohort) <- 
  c(
    crt_log = "log [Creatinine (micromol/L)]",
    st_deviation = "ST deviation",
    smoking_cessation_advice = "Received smoking cessation advice",
    aspirin = "Discharged on aspirin",
    bb      = "Discharged on beta blocker",
    statin  = "Discharged on statin",
    ace     = "Discharged on ACE inhibitor",
    thieno  = "Discharged on thienopyridine",
    tica    = "Discharged on ticagrelor",
    angiogram_eligibility = "Angiogram eligibility",
    angiogram_receipt     = "Angiogram receipt",
    angio_within_72h      = "Angiogram within 72 hrs"
  )

# Create binary SMI variable
cohort <-
  cohort %>%
  mutate(
    smi_bin =
      case_when(
        smi %in% c("Schizophrenia", "Bipolar disorder", "Depression") ~ "Mental illness",
        smi %in% "No SMI" ~ "No mental illness"
      ),
    smi_bin = factor(smi_bin, levels = c("No mental illness", "Mental illness"))
  )

```

# Background
This CCU046_01 output includes descriptive tables prepared for a publication about severe mental illness and receipt of care following myocardial infarction.The output has been created from Myocardial Ischaemia National Audit Project (MINAP) data linked to HES, GDPPR, death records and COVID-19 surveillance data.

# Key cohorts

```{r nstemi_key, results = "asis"}

# Full cohort
nstemi <- filter(cohort, mi_type %in% "NSTEMI")
nstemi_n <- nstemi %>% nrow()

# Define complete cases flags
nstemi <- 
  nstemi %>%
  mutate(
    cc = !is.na(imd_2019) & !is.na(ethnic_5) & !is.na(cardiogenic_shock) &
         !is.na(ecg) & !is.na(cardiac_arrest) &  !is.na(creatinine) &
         !is.na(sbp) & !is.na(heart_rate) &  !is.na(procode3),
    cc2 = !is.na(imd_2019) & !is.na(ethnic_5) & !is.na(procode3)
  )

# Full cohort, complete cases 
nstemi_cc <- nstemi %>% filter(cc)
nstemi_cc_n <- nstemi_cc %>% nrow()

# Full cohort, complete cases (sensitivity analysis)
nstemi_cc2   <- nstemi %>% filter(cc2)
nstemi_cc2_n <- nstemi_cc2 %>% nrow()

# Angiogram eligibility: angiogram eligibility not missing --------------------
nstemi_angel <- filter(nstemi, !is.na(angiogram_eligibility))
nstemi_angel_n <- nstemi_angel %>% nrow()

# Angiogram eligibility, complete cases
nstemi_angel_cc <- nstemi_angel %>% filter(cc)
nstemi_angel_cc_n <- nstemi_angel_cc %>% nrow()

# Angiogram eligibility, complete cases (sensitivity analysis)
nstemi_angel_cc2 <- nstemi_angel %>% filter(cc2)
nstemi_angel_cc2_n <- nstemi_angel_cc2 %>% nrow()

# Angiogram receipt: people eligible for an angiogram -------------------------
nstemi_angrec <- filter(nstemi, angiogram_eligibility %in% "Yes")
nstemi_angrec_n <- nstemi_angrec %>% nrow()

nstemi_angrec_cc <- nstemi_angrec %>% filter(cc)
nstemi_angrec_cc_n <- nstemi_angrec_cc %>% nrow()

nstemi_angrec_cc2 <- nstemi_angrec %>% filter(cc2)
nstemi_angrec_cc2_n <- nstemi_angrec_cc2 %>% nrow()

# Angiogram within 72 hours ---------------------------------------------------
# - People who received an angiogram, angiogram within 72 hours not missing 
nstemi_ang72 <- filter(nstemi, 
                       angiogram_receipt %in% "Yes",
                       angio_within_72h %in% c("Yes", "No"))
nstemi_ang72_n <- nstemi_ang72 %>% nrow()

nstemi_ang72_cc <- nstemi_ang72 %>% filter(cc)
nstemi_ang72_cc_n <- nstemi_ang72_cc %>% nrow()

nstemi_ang72_cc2 <- nstemi_ang72 %>% filter(cc2)
nstemi_ang72_cc2_n <- nstemi_ang72_cc2 %>% nrow()

# Admission to cardiac ward ---------------------------------------------------
# - Admission to cardiac ward variable not recorded as died in A&E;
# - Admission to cardiac ward not missing

nstemi_ward <- nstemi %>% filter(admission_to_cardiac_ward %in% c("Yes", "No"))
nstemi_ward_n <- nstemi_ward %>% nrow()

nstemi_ward_cc <- nstemi_ward %>% filter(cc)
nstemi_ward_cc_n <- nstemi_ward_cc %>% nrow()

nstemi_ward_cc2 <- nstemi_ward %>% filter(cc2)
nstemi_ward_cc2_n <- nstemi_ward_cc2 %>% nrow()

# Cardiac rehabilitation ------------------------------------------------------
# - Discharged home, cardiac rehab yes /no / patient declined
nstemi_rehab <- nstemi %>% 
                filter(discharge_destination %in% "Home",
                       cardiac_rehab %in% c("Yes", "No", "Patient declined"))
nstemi_rehab_n <- nstemi_rehab %>% nrow()

nstemi_rehab_cc <- filter(nstemi_rehab, cc)
nstemi_rehab_cc_n <- nstemi_rehab_cc %>% nrow()

nstemi_rehab_cc2 <- filter(nstemi_rehab, cc2)
nstemi_rehab_cc2_n <- nstemi_rehab_cc2 %>% nrow()

# Secondary prevention --------------------------------------------------------
# - Discharged home, secondary prevention not missing
nstemi_prev <- nstemi %>%
               filter(discharge_destination %in% "Home",
                      !is.na(prev_all))
nstemi_prev_n <- nstemi_prev %>% nrow()

nstemi_prev_cc <- nstemi_prev %>% filter(cc)
nstemi_prev_cc_n <- nstemi_prev_cc %>% nrow()

nstemi_prev_cc2 <- nstemi_prev %>% filter(cc2)
nstemi_prev_cc2_n <- nstemi_prev_cc2 %>% nrow()

# Smoking advice --------------------------------------------------------------
# - Smokers, discharged home, smoking cessation advice recorded
nstemi_smk <- 
  nstemi %>%
  filter(
    discharge_destination %in% "Home",
    smoking_cat %in% "Current smoker", 
    smoking_cessation_advice %in% c("Yes", "Planned in rehab", "No")
  )
nstemi_smk_n <- nstemi_smk %>% nrow()

nstemi_smk_cc <- nstemi_smk %>% filter(cc)
nstemi_smk_cc_n <- nstemi_smk_cc %>% nrow()

nstemi_smk_cc2 <- nstemi_smk %>% filter(cc2)
nstemi_smk_cc2_n <- nstemi_smk_cc2 %>% nrow()

# Create table
key_cohorts <- 
  data.frame(
    cohort = c("Full cohort", "Angiogram eligibility", "Receipt of angiogram",
               "Angiogram within 72 hrs", "Admission to cardiac ward", 
               "Cardiac rehabilitation", "Secondary prevention medication",
               "Smoking advice"),
    n = c(nstemi_n, nstemi_angel_n, nstemi_angrec_n, nstemi_ang72_n, 
          nstemi_ward_n, nstemi_rehab_n, nstemi_prev_n,   nstemi_smk_n),
    n_cc = c(nstemi_cc_n, nstemi_angel_cc_n, nstemi_angrec_cc_n, nstemi_ang72_cc_n, 
             nstemi_ward_cc_n, nstemi_rehab_cc_n, nstemi_prev_cc_n, nstemi_smk_cc_n),
    n_cc2 = c(nstemi_cc2_n, nstemi_angel_cc2_n, nstemi_angrec_cc2_n, nstemi_ang72_cc2_n, 
              nstemi_ward_cc2_n, nstemi_rehab_cc2_n, nstemi_prev_cc2_n, nstemi_smk_cc2_n)
  )

key_cohorts <- 
  key_cohorts %>%
  mutate(
    n_rnd = rnd5(n),
    #
    n_cc_rnd = rnd5(n_cc),
    per_cc = round(100*n_cc_rnd/n_rnd, digits = 1),
    n_cc_rnd_fmt = paste0(format(n_cc_rnd, digits=6), " (", per_cc, "%)"),
    #
    n_cc2_rnd = rnd5(n_cc2),
    per_cc2 = round(100*n_cc2_rnd/n_rnd, digits = 1),
    n_cc2_rnd_fmt = paste0(format(n_cc2_rnd, digits=6), " (", per_cc2, "%)")
  )

kable(
  select(key_cohorts, cohort, n_rnd, n_cc_rnd_fmt, n_cc2_rnd_fmt), 
  caption = "NSTEMI: Key cohorts",
  col.names = c("Cohort", "N", "Complete cases", "Complete cases (SA)")
)
```

For the main analyses, the complete cases are based on IMD decile, ethnicity, cardiogenic shock, ECG determining treatment, cardiac arrest, creatinine, SBP, heart rate
and hospital.

In a sensitivity analysis (SA) excluding the MI characteristics, the complete cases analyses are based on IMD decile, ethnicity and hospital only.

```{r nstemi_smi, results = "asis"}

# Function to create summary of cohort by smi
smi_fun <- function(df) {
  
  df_n <- nrow(df)
  
  out <- 
    df %>% 
    tabyl(smi) %>% 
    adorn_pct_formatting() %>%
    mutate(
      n_rnd = rnd5(n),
      per_rnd = round(100*n_rnd/df_n, digits=1),
      n_rnd_fmt = paste0(n_rnd, " (", per_rnd, "%)")
    )
  
  out <- pull(out, n_rnd_fmt)
  out
  
}

nstemi_smi            <- smi_fun(nstemi)
nstemi_cc_smi         <- smi_fun(nstemi_cc)
nstemi_cc2_smi        <- smi_fun(nstemi_cc2)

nstemi_angel_smi      <- smi_fun(nstemi_angel)
nstemi_angel_cc_smi   <- smi_fun(nstemi_angel_cc)
nstemi_angel_cc2_smi  <- smi_fun(nstemi_angel_cc2)

nstemi_angrec_smi     <- smi_fun(nstemi_angrec)
nstemi_angrec_cc_smi  <- smi_fun(nstemi_angrec_cc)
nstemi_angrec_cc2_smi <- smi_fun(nstemi_angrec_cc2)

nstemi_ang72_smi      <- smi_fun(nstemi_ang72)
nstemi_ang72_cc_smi   <- smi_fun(nstemi_ang72_cc)
nstemi_ang72_cc2_smi  <- smi_fun(nstemi_ang72_cc2)

nstemi_ward_smi       <- smi_fun(nstemi_ward)
nstemi_ward_cc_smi    <- smi_fun(nstemi_ward_cc)
nstemi_ward_cc2_smi   <- smi_fun(nstemi_ward_cc2)

nstemi_rehab_smi      <- smi_fun(nstemi_rehab)
nstemi_rehab_cc_smi   <- smi_fun(nstemi_rehab_cc)  
nstemi_rehab_cc2_smi  <- smi_fun(nstemi_rehab_cc2) 

nstemi_prev_smi      <- smi_fun(nstemi_prev)
nstemi_prev_cc_smi   <- smi_fun(nstemi_prev_cc)  
nstemi_prev_cc2_smi  <- smi_fun(nstemi_prev_cc2)  

nstemi_smk_smi      <- smi_fun(nstemi_smk)
nstemi_smk_cc_smi   <- smi_fun(nstemi_smk_cc)  
nstemi_smk_cc2_smi  <- smi_fun(nstemi_smk_cc2)  

# NSTEMI cohorts by SMI
nstemi_cohorts_smi <- 
  rbind(
    nstemi_smi,
    nstemi_cc_smi,
    nstemi_cc2_smi,
    #
    nstemi_angel_smi, 
    nstemi_angel_cc_smi,
    nstemi_angel_cc2_smi,
    #
    nstemi_angrec_smi, 
    nstemi_angrec_cc_smi,
    nstemi_angrec_cc2_smi,
    #
    nstemi_ang72_smi,
    nstemi_ang72_cc_smi,
    nstemi_ang72_cc2_smi,
    #
    nstemi_ward_smi,
    nstemi_ward_cc_smi,
    nstemi_ward_cc2_smi,
    #
    nstemi_rehab_smi, 
    nstemi_rehab_cc_smi,
    nstemi_rehab_cc2_smi, 
    #
    nstemi_prev_smi, 
    nstemi_prev_cc_smi,
    nstemi_prev_cc2_smi, 
    #
    nstemi_smk_smi, 
    nstemi_smk_cc_smi,
    nstemi_smk_cc2_smi
  )

colnames(nstemi_cohorts_smi) <- 
  c("Schizophrenia", "Bipolar disorder", "Depression", "No SMI")

nstemi_cohorts_smi <- 
  as.data.frame(nstemi_cohorts_smi) %>%
  mutate(
    Cohort = rep(c("Full cohort", "Angiogram eligibility", "Receipt of angiogram",
        "Angiogram within 72 hrs", "Admission to cardiac ward", 
        "Cardiac rehabilitation", "Secondary prevention medication",
        "Smoking advice"),
                 each = 3),
    Including = rep(c("All", "CC", "CC (SA)"), times = 8)
  ) %>%
  select(Cohort, Including, Schizophrenia, `Bipolar disorder`, Depression, `No SMI`)

kable(
  nstemi_cohorts_smi,
  caption = "NSTEMI cohorts by SMI",
  row.names = FALSE
)
```
CC: complete cases, CC: complete cases (sensitivity analysis)

# Full cohort (including missing data)

```{r nstemi_base, results = "asis"}

tab1_cntrls <-
  tableby.control(
    numeric.stats = c("meansd" ,"medianrange_kf" , "n_per_miss_5"),
    cat.stats = c("countpct_5"),
    cat.simplify = FALSE
  )

# Baseline characteristics table based on full NSTEMI cohort
tab1_nstemi <-
  tableby(
    smi ~
      age_mi + sex +
      includeNA(imd_2019, label = "Missing") +
      includeNA(ethnic_5, label = "Missing") +
      mi_event_year + mi_wd + mi_on + procode3_miss +
      comorb_angina + comorb_mi +
      hx_pci +
      comorb_hf +  comorb_diab +
      comorb_crf + comorb_cevd +
      includeNA(cardiogenic_shock, label = "Missing") +
      includeNA(ecg, label = "Missing") +
      includeNA(st_deviation, label = "Missing") +
      includeNA(cardiac_arrest, label = "Missing") +
      includeNA(cardiac_enzymes_elevated, label = "Missing") +
      creatinine + crt_log + sbp + heart_rate +
      covid +
      includeNA(bmi_cat) + includeNA(smoking_cat) +
      includeNA(discharge_destination) + 
      includeNA(angiogram_eligibility) + 
      includeNA(angiogram_receipt) + 
      includeNA(angio_within_72h) + 
      includeNA(admission_to_cardiac_ward) + 
      includeNA(cardiac_rehab) + 
      includeNA(prev_all) + 
      includeNA(aspirin) + 
      includeNA(bb) + 
      includeNA(statin) + 
      includeNA(ace) + 
      includeNA(thieno) + 
      includeNA(tica) +
      includeNA(smoking_cessation_advice),
    data = nstemi,
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(meansd = 'Mean (SD)',
           medianrange_kf = 'Median [IQR]',
           n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab1_nstemi$tables$smi$y$stats <- 5*round(tab1_nstemi$tables$smi$y$stats/5)

summary(
  tab1_nstemi,
  title = "Baseline characteristics for the NSTEMI cohort, counts rounded to the nearest 5")

write.csv(
  summary(tab1_nstemi, text = NULL),
  file = file.path(bc_folder, "02_nstemi_full_baseline.csv")
)
```

# Outcomes

## Angiogram eligibility

```{r out_angel, results = "asis"}

tab_angel <-
  tableby(
    smi ~ includeNA(angiogram_eligibility),
    data = nstemi,
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_angel$tables$smi$y$stats <- 5*round(tab_angel$tables$smi$y$stats/5)

summary(tab_angel,
        title = "Angiogram eligibility, counts rounded to the nearest 5")

# Repeat excluding missing
tab_angel_cc <-
  tableby(
    smi ~ angiogram_eligibility,
    data = filter(nstemi, !is.na(angiogram_eligibility)),
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_angel_cc$tables$smi$y$stats <- 5*round(tab_angel_cc$tables$smi$y$stats/5)

summary(tab_angel_cc,
        title = "Angiogram eligibility, counts rounded to the nearest 5")
```

## Angiogram receipt

```{r out_angrec, results = "asis"}

# Summary of angiogram receipt amongst eligible patients
tab_angrec <-
  tableby(
    smi ~ includeNA(angiogram_receipt),
    data = nstemi_angrec,
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_angrec$tables$smi$y$stats <- 5*round(tab_angrec$tables$smi$y$stats/5)

summary(tab_angrec,
        title = "Angiogram receipt amongst patients eligible for an angiogram, counts rounded to the nearest 5")
```

## Coronary intervention

```{r out_corint, results = "asis"}

ci_lvls <- c("Percutaneous coronary intervention", "CABG",
             "PCI planned after discharge", "CABG planned after discharge", 
             "Not applicable", "Patient refused", "Not performed or arranged")

nstemi <- 
  nstemi %>%
  mutate(
    coronary_intervention = substring(coronary_intervention, 4, 1000),
    coronary_intervention = ifelse(coronary_intervention %in% "Unknown", NA, coronary_intervention),
    coronary_intervention = factor(coronary_intervention, levels = ci_lvls)
  )


# Summary of coronary intervention amongst people who received angiography
tab_corint <-
  tableby(
    smi ~ includeNA(coronary_intervention),
    data = filter(nstemi, angiogram_receipt %in% "Yes"),
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )


tab_corint$tables$smi$y$stats <- 5*round(tab_corint$tables$smi$y$stats/5)

summary(
  tab_corint,
  title = "Coronary intervention amongst patients who received angiogram, counts rounded to the nearest 5")

## Repeat excluding missing

tab_corint_cc <-
  tableby(
    smi ~ coronary_intervention,
    data = filter(nstemi, angiogram_receipt %in% "Yes" & !is.na(coronary_intervention)),
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )


tab_corint_cc$tables$smi$y$stats <- 5*round(tab_corint_cc$tables$smi$y$stats/5)

summary(
  tab_corint_cc,
  title = "Coronary intervention amongst patients who received angiogram, counts rounded to the nearest 5")


```

## Angiogram within 72 hours

```{r out_ang72, results = "asis"}

nstemi_ang72_out <- 
  filter(nstemi, angiogram_receipt %in% "Yes") %>%
  mutate(
    angio_within_72h = ifelse(angio_within_72h %in% "Unknown", NA, angio_within_72h)
  )

# Summary of angiogram within 72 hrs amongst people who received angiography
tab_ang72 <-
  tableby(
    smi ~ includeNA(angio_within_72h),
    data = nstemi_ang72_out,
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_ang72$tables$smi$y$stats <- 5*round(tab_ang72$tables$smi$y$stats/5)

summary(tab_ang72,
        title = "Angiogram within 72 hours amongst patients who received angiogram, counts rounded to the nearest 5")

# Repeat excluding misisng
tab_ang72_cc <-
  tableby(
    smi ~ angio_within_72h,
    data = filter(nstemi_ang72_out, !is.na(angio_within_72h)),
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_ang72_cc$tables$smi$y$stats <- 5*round(tab_ang72_cc$tables$smi$y$stats/5)

summary(tab_ang72_cc,
        title = "Angiogram within 72 hours amongst patients who received angiogram, counts rounded to the nearest 5")
```

## Admission to cardiac ward

```{r out_ward, results = "asis"}

nstemi_ward_out <- filter(nstemi, !admission_to_cardiac_ward %in% "Died_in_A&E")

# Summary of admission to cardiac ward among patients who did not die in A&E
tab_ward <-
  tableby(
    smi ~ includeNA(admission_to_cardiac_ward),
    data = nstemi_ward_out,
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_ward$tables$smi$y$stats <- 5*round(tab_ward$tables$smi$y$stats/5)

summary(
  tab_ward,
  title = "Admission to cardiac ward amongst patients who did not die in A&E, counts rounded to the nearest 5")

# Repeat excluding missing
tab_ward_cc <-
  tableby(
    smi ~ admission_to_cardiac_ward,
    data = filter(nstemi_ward_out, !is.na(admission_to_cardiac_ward)),
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_ward_cc$tables$smi$y$stats <- 5*round(tab_ward_cc$tables$smi$y$stats/5)

summary(
  tab_ward_cc,
  title = "Admission to cardiac ward amongst patients who did not die in A&E, counts rounded to the nearest 5")
```

## Referred for cardiac rehabilitation

```{r out_rehab, results = "asis"}

# Two ways to look at cardiac rehab:
# - Including people who were not indicated (e.g. due to severe comorb)
# - Exclude the above group, as per the analyses
# For info, present both ways

# Option 1 -----------------------
nstemi_rehab_out <- filter(nstemi, discharge_destination %in% "Home")

tab_rehab <-
  tableby(
    smi ~ includeNA(cardiac_rehab),
    data = nstemi_rehab_out,
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_rehab$tables$smi$y$stats <- 5*round(tab_rehab$tables$smi$y$stats/5)

summary(tab_rehab,
        title = "Referral for cardiac rehab amongst patients discharged home, counts rounded to the nearest 5")

# Option 2 ---------------
nstemi_rehab_out2 <- 
  filter(nstemi, 
         discharge_destination %in% "Home",
         !cardiac_rehab %in% "Not indicated")

tab_rehab2 <-
  tableby(
    smi ~ includeNA(cardiac_rehab),
    data = nstemi_rehab_out2,
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_rehab2$tables$smi$y$stats <- 5*round(tab_rehab2$tables$smi$y$stats/5)

summary(
  tab_rehab2,
  title = "Referral for cardiac rehab amongst patients discharged home and without cardiac rehabilitation recorded as 'Not indicated', counts rounded to the nearest 5")

# Repeat option 2 excluding missing
tab_rehab2_cc <-
  tableby(
    smi ~ cardiac_rehab,
    data = filter(nstemi_rehab_out2, !is.na(cardiac_rehab)),
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_rehab2_cc$tables$smi$y$stats <- 5*round(tab_rehab2_cc$tables$smi$y$stats/5)

summary(tab_rehab2_cc,
        title = "Referral for cardiac rehab amongst patients discharged home and without cardiac rehabilitation recorded as 'Not indicated', counts rounded to the nearest 5")
```

## Discharged on all secondary prevention medications

```{r out_prev, results = "asis"}

nstemi_prev_out <- filter(nstemi, discharge_destination %in% "Home") 

# Summary of secondary prevention medication amongst people discharged home
tab_prev <-
  tableby(
    smi ~ includeNA(prev_all),
    data = nstemi_prev_out,
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_prev$tables$smi$y$stats <- 5*round(tab_prev$tables$smi$y$stats/5)

summary(tab_prev,
        title = "Receipt of all secondary prevention medication amongst patients discharged home, counts rounded to the nearest 5")

# Repeat excluding missing
tab_prev <-
  tableby(
    smi ~ prev_all,
    data = filter(nstemi_prev_out, !is.na(prev_all)),
    control = tab1_cntrls,
    digits = 1,
    stats.labels =
      list(n_per_miss = 'Missing',
           n_per_miss_5 = 'Missing',
           Nmiss = 'Missing')
  )
tab_prev$tables$smi$y$stats <- 5*round(tab_prev$tables$smi$y$stats/5)

summary(
  tab_prev,
  title = "Receipt of all secondary prevention medication amongst patients discharged home, counts rounded to the nearest 5")
```

## Summary of outcomes by month

```{r out_month, results = "asis"}

# Count of NSTEMI by month
nstemi_month_adm <- 
  nstemi %>%
  tabyl(mi_event_month) %>%
  mutate(
    outcome = "MI admissions (N)",
    n_per = rnd5(n)
  ) %>%
  select(outcome, mi_event_month, n_per)

# Angiogram eligibility
nstemi_month_angel <-
  filter(nstemi, !is.na(angiogram_eligibility)) %>%
  tabyl(mi_event_month, angiogram_eligibility) %>%
  mutate(
    outcome = "Angiography eligibility (%)",
    total = No + Yes,
    n_per = 100*rnd5(Yes)/rnd5(total)
  ) %>%
  select(outcome, mi_event_month, n_per)

# Angiogram receipt
nstemi_month_angrec <-
  nstemi_angrec %>%
  tabyl(mi_event_month, angiogram_receipt) %>%
  mutate(
    outcome = "Angiography receipt (%)",
    total = No + Yes + `Patient refused`,
    n_per = 100*rnd5(Yes)/rnd5(total)
  ) %>%
  select(outcome, mi_event_month, n_per)

# Angiogram within 72 hours
nstemi_month_ang72 <- 
  filter(nstemi_ang72_out, !is.na(angio_within_72h)) %>%
  tabyl(mi_event_month, angio_within_72h) %>%
  mutate(
    outcome = "Angiography within 72 hrs (%)",
    total = Yes + No, 
    n_per = 100*rnd5(Yes)/rnd5(total)
  ) %>%
  select(outcome, mi_event_month, n_per)

# Admission to cardiac ward
nstemi_month_ward <- 
  filter(nstemi_ward_out, !is.na(admission_to_cardiac_ward)) %>%
  tabyl(mi_event_month, admission_to_cardiac_ward) %>%
  mutate(
    outcome = "Admission to cardiac ward (%)",
    total = Yes + No, 
    n_per = 100*rnd5(Yes)/rnd5(total)
  ) %>%
  select(outcome, mi_event_month, n_per)

# Referral for cardiac rehabilitation
nstemi_month_rehab <- 
  filter(nstemi_rehab_out2, !is.na(cardiac_rehab)) %>%
  tabyl(mi_event_month, cardiac_rehab) %>%
  mutate(
    outcome = "Referral for rehabilitation (%)",
    total = Yes + No + `Patient declined`,
    n_per = 100*rnd5(Yes)/rnd5(total)
  ) %>%
  select(outcome, mi_event_month, n_per)
  
# Secondary prevention medication
nstemi_month_prev <- 
  filter(nstemi_prev_out, !is.na(prev_all)) %>%
  tabyl(mi_event_month, prev_all) %>%
  mutate(
    outcome = "Secondary prevention (%)", 
    total = Yes + No,
    n_per = 100*rnd5(Yes)/rnd5(total)
  ) %>%
  select(outcome, mi_event_month, n_per)
  
# Collate outcomes by month
nstemi_month <- 
  bind_rows(
    nstemi_month_adm,
    nstemi_month_angel,
    nstemi_month_angrec, 
    nstemi_month_ang72,
    nstemi_month_ward,
    nstemi_month_rehab, 
    nstemi_month_prev
  ) %>%
  mutate(
    outcome = 
      factor(
        outcome, 
        levels = c("MI admissions (N)", "Angiography eligibility (%)", "Angiography receipt (%)",
                   "Angiography within 72 hrs (%)", "Admission to cardiac ward (%)", 
                   "Referral for rehabilitation (%)", "Secondary prevention (%)")
      )
  )

# Save outcomes by month
write.csv(
  nstemi_month, 
  file.path(bc_folder, "02_nstemi_month.csv"),
  row.names = FALSE
)

nstemi_month_plot <- 
ggplot(nstemi_month, aes(x = mi_event_month, y = n_per)) + 
  geom_line() + 
  facet_wrap(
    vars(outcome),
    ncol = 1,
    scales = "free_y",
    strip.position = "top"
  ) +
  facetted_pos_scales(
    y = 
      list(
        NULL,
        scale_y_continuous(limits = c(80, 91.6)), 
        scale_y_continuous(limits = c(80, 91.6)), 
        NULL,
        NULL,
        scale_y_continuous(limits = c(80, 91.6)), 
        scale_y_continuous(limits = c(80, 91.6))
      )
  ) +
  scale_x_date(date_labels = "%h %Y", expand = c(0,0)) + 
  theme_bw() + 
  theme(
    strip.background = element_rect(fill = "white"),
    panel.spacing = unit(0 , 'lines')
  ) + 
  labs(x = "Month", y = "")

nstemi_month_plot
```

## Summary of outcomes by 4-month period

```{r out_period, results = "asis"}

# Count of NSTEMI by period and SMI
nstemi_per_adm <- 
  nstemi %>%
  group_by(period_4, smi) %>%
  summarise(
    n = n()
  ) %>%
  mutate(
    outcome = "MI admissions (N)",
    n_per = rnd5(n)
  ) %>%
  select(outcome, period_4, smi, n_per)

# Angiogram eligibility
nstemi_per_angel <-
  filter(nstemi, !is.na(angiogram_eligibility)) %>%
  group_by(period_4, smi) %>%
  summarise(
    outcome = "Angiography eligibility (%)",
    total = n(),
    Yes = sum(angiogram_eligibility %in% "Yes"),
    n_per = 100*Yes/total
  ) %>%
  select(outcome, period_4, smi, n_per)
  
# Angiogram receipt
nstemi_per_angrec <-
  nstemi_angrec %>%
  group_by(period_4, smi) %>%
  summarise(
    outcome = "Angiography receipt (%)",
    total = n(), 
    Yes = sum(angiogram_receipt %in% "Yes"),
    n_per = 100*Yes/total
  )%>%
  select(outcome, period_4, smi, n_per)

# Angiogram within 72 hours
nstemi_per_ang72 <- 
  filter(nstemi_ang72_out, !is.na(angio_within_72h)) %>%
  group_by(period_4, smi) %>%
  summarise(
    outcome = "Angiography within 72 hrs (%)",
    total = n(),
    Yes = sum(angio_within_72h %in% "Yes"),
    n_per = 100*Yes/total
  ) %>%
  select(outcome, period_4, smi, n_per)

# Admission to cardiac ward
nstemi_per_ward <- 
  filter(nstemi_ward_out, !is.na(admission_to_cardiac_ward)) %>%
  group_by(period_4, smi) %>%
  summarise(
    outcome = "Admission to cardiac ward (%)",
    total = n(),
    Yes = sum(admission_to_cardiac_ward %in% "Yes"),
    n_per = 100*Yes/total
  ) %>%
  select(outcome, period_4, smi, n_per)
  
# Referral for cardiac rehabilitation
nstemi_per_rehab <- 
  filter(nstemi_rehab_out2, !is.na(cardiac_rehab)) %>%
  group_by(period_4, smi) %>%
  summarise(
    outcome = "Referral for rehabilitation (%)",
    total = n(), 
    Yes = sum(cardiac_rehab %in% "Yes"),
    n_per = 100*Yes/total
  ) %>%
  select(outcome, period_4, smi, n_per)
  
# Secondary prevention medication
nstemi_per_prev <- 
  filter(nstemi_prev_out, !is.na(prev_all)) %>%
  group_by(period_4, smi) %>%
  summarise(
    outcome = "Secondary prevention (%)",
    total = n(), 
    Yes = sum(prev_all %in% "Yes"),
    n_per = 100*Yes/total
  ) %>%
  select(outcome, period_4, smi, n_per)
  
# Collate outcomes by month
nstemi_per <- 
  bind_rows(
    nstemi_per_adm,
    nstemi_per_angel,
    nstemi_per_angrec, 
    nstemi_per_ang72,
    nstemi_per_ward,
    nstemi_per_rehab, 
    nstemi_per_prev
  ) %>%
  mutate(
    outcome = factor(outcome, 
                     levels = c("MI admissions (N)", "Angiography eligibility (%)",
                                "Angiography receipt (%)", "Angiography within 72 hrs (%)",
                                "Admission to cardiac ward (%)", "Referral for rehabilitation (%)",
                                "Secondary prevention (%)")),
    period_4_start = paste("1", substring(period_4, 1, 8)),
    period_4_date = as.Date(period_4_start, format = "%d %b %Y"),
  )

# Save outcomes by month
write.csv(
  nstemi_per, 
  file.path(bc_folder, "02_nstemi_period_smi.csv"),
  row.names = FALSE
)

nstemi_per_plot <- 
  ggplot(nstemi_per, aes(x = period_4_date, y = n_per, color = smi)) + 
  geom_line() + 
  facet_wrap(
    vars(outcome),
    ncol = 1,
    scales = "free_y",
    strip.position = "top"
  ) +
  scale_x_date(date_labels = "%h %Y", expand = c(0,0)) + 
  theme_bw() + 
  theme(
    strip.background = element_rect(fill = "white"),
    panel.spacing = unit(0 , 'lines')
  ) + 
  labs(x = "Month", y = "")

nstemi_per_plot
```

## Summary of outcomes by 4-month period (binary SMI)

```{r out_period_bin, results = "asis"}

# Count of NSTEMI by period and SMI
nstemi_per_bin_adm <- 
  nstemi %>%
  group_by(period_4, smi_bin) %>%
  summarise(
    n = n()
  ) %>%
  mutate(
    outcome = "MI admissions (N)",
    n_per = rnd5(n)
  ) %>%
  select(outcome, period_4, smi_bin, n_per)

# Angiogram eligibility
nstemi_per_bin_angel <-
  filter(nstemi, !is.na(angiogram_eligibility)) %>%
  group_by(period_4, smi_bin) %>%
  summarise(
    outcome = "Angiography eligibility (%)",
    total = n(),
    Yes = sum(angiogram_eligibility %in% "Yes"),
    n_per = 100*Yes/total,
    n_per_low = 100*prop.test(Yes, total)$conf.int[1],
    n_per_upp = 100*prop.test(Yes, total)$conf.int[2]
  ) %>%
  select(outcome, period_4, smi_bin, n_per, n_per_low, n_per_upp)

# Angiogram receipt
nstemi_per_bin_angrec <-
  nstemi_angrec %>%
  group_by(period_4, smi_bin) %>%
  summarise(
    outcome = "Angiography receipt (%)",
    total = n(), 
    Yes = sum(angiogram_receipt %in% "Yes"),
    n_per = 100*Yes/total,
    n_per_low = 100*prop.test(Yes, total)$conf.int[1],
    n_per_upp = 100*prop.test(Yes, total)$conf.int[2]
  )%>%
  select(outcome, period_4, smi_bin, n_per, n_per_low, n_per_upp)

# Angiogram within 72 hours
nstemi_per_bin_ang72 <- 
  filter(nstemi_ang72_out, !is.na(angio_within_72h)) %>%
  group_by(period_4, smi_bin) %>%
  summarise(
    outcome = "Angiography within 72 hrs (%)",
    total = n(),
    Yes = sum(angio_within_72h %in% "Yes"),
    n_per = 100*Yes/total,
    n_per_low = 100*prop.test(Yes, total)$conf.int[1],
    n_per_upp = 100*prop.test(Yes, total)$conf.int[2]
  ) %>%
  select(outcome, period_4, smi_bin, n_per, n_per_low, n_per_upp)

# Admission to cardiac ward
nstemi_per_bin_ward <- 
  filter(nstemi_ward_out, !is.na(admission_to_cardiac_ward)) %>%
  group_by(period_4, smi_bin) %>%
  summarise(
    outcome = "Admission to cardiac ward (%)",
    total = n(),
    Yes = sum(admission_to_cardiac_ward %in% "Yes"),
    n_per = 100*Yes/total,
    n_per_low = 100*prop.test(Yes, total)$conf.int[1],
    n_per_upp = 100*prop.test(Yes, total)$conf.int[2]
  ) %>%
  select(outcome, period_4, smi_bin, n_per, n_per_low, n_per_upp)

# Referral for cardiac rehabilitation
nstemi_per_bin_rehab <- 
  filter(nstemi_rehab_out2, !is.na(cardiac_rehab)) %>%
  group_by(period_4, smi_bin) %>%
  summarise(
    outcome = "Referral for rehabilitation (%)",
    total = n(), 
    Yes = sum(cardiac_rehab %in% "Yes"),
    n_per = 100*Yes/total,
    n_per_low = 100*prop.test(Yes, total)$conf.int[1],
    n_per_upp = 100*prop.test(Yes, total)$conf.int[2]
  ) %>%
  select(outcome, period_4, smi_bin, n_per, n_per_low, n_per_upp)


# Secondary prevention medication
nstemi_per_bin_prev <- 
  filter(nstemi_prev_out, !is.na(prev_all)) %>%
  group_by(period_4, smi_bin) %>%
  summarise(
    outcome = "Secondary prevention (%)",
    total = n(), 
    Yes = sum(prev_all %in% "Yes"),
    n_per = 100*Yes/total,
    n_per_low = 100*prop.test(Yes, total)$conf.int[1],
    n_per_upp = 100*prop.test(Yes, total)$conf.int[2]
  ) %>%
  select(outcome, period_4, smi_bin, n_per, n_per_low, n_per_upp)

# Collate outcomes by month
nstemi_per_bin <- 
  bind_rows(
    nstemi_per_bin_adm,
    nstemi_per_bin_angel,
    nstemi_per_bin_angrec, 
    nstemi_per_bin_ang72,
    nstemi_per_bin_ward,
    nstemi_per_bin_rehab, 
    nstemi_per_bin_prev
  ) %>%
  mutate(
    outcome = 
      factor(
        outcome, 
        levels = c("MI admissions (N)", "Angiography eligibility (%)", "Angiography receipt (%)",
                   "Angiography within 72 hrs (%)", "Admission to cardiac ward (%)", 
                   "Referral for rehabilitation (%)", "Secondary prevention (%)")
      ),
    period_4_start = paste("1", substring(period_4, 1, 8)),
    period_4_date = as.Date(period_4_start, format = "%d %b %Y"),
  )

# Save outcomes by month
write.csv(
  nstemi_per_bin, 
  file.path(bc_folder, "02_nstemi_period_smi_bin.csv"),
  row.names = FALSE
)

nstemi_per_bin_plot <- 
  ggplot(nstemi_per_bin, aes(x = period_4_date, y = n_per, color = smi_bin)) + 
  geom_line() + 
  facet_wrap(
    vars(outcome),
    ncol = 1,
    scales = "free_y",
    strip.position = "top"
  ) +
  scale_x_date(
    date_labels = "%h %Y",
    expand = c(0,0)
  ) + 
  theme_bw() + 
  theme(
    strip.background = element_rect(fill = "white"),
    panel.spacing = unit(0 , 'lines')
  ) + 
  labs(
    x = "Month", 
    y = ""
  )

nstemi_per_bin_plot

```
